---
title: "final project1 viruses ziying,lu"
output: html_document
---

## 1. library
```{r}
library(readxl)
library(tidyverse)
library(maps)
library(mapdata)
library(ggmap)
library(mapproj)
library(lme4)
library(sp)
library(maptools)
library(magrittr)
library(plyr)
library(gridExtra)
library(ggplot2)
library(tableone)
library(nnet)
library(stargazer)
library(devtools)
library(ggpubr)
```

## 2. load data
```{r}
Data_for_enteric_virus <- read_excel("Data for enteric virus.xlsx")
attach(Data_for_enteric_virus)
```

## 3. data processing
```{r}
name <- as.vector(colnames(Data_for_enteric_virus))
```

## 4 SiteRecruitment (change number to specific name)
```{r}
Site_recruitment <- ifelse(Data_for_enteric_virus$SiteRecruitment == 4,"Dong Thap", ifelse(Data_for_enteric_virus$SiteRecruitment == 2,"Dak Lak",ifelse(Data_for_enteric_virus$SiteRecruitment == 5,"Hue","Khanh Hoa")))
Data_for_enteric_virus$SiteRecruitment <- Site_recruitment 
```

## 5. data frame（the distance from home to hospital）
```{r}
map_distance <- data.frame(lon=Data_for_enteric_virus$LONGITUDE,lat=Data_for_enteric_virus$LATITUDE,
                            hospital=Data_for_enteric_virus$SiteRecruitment, lon_1=Data_for_enteric_virus$SiteRecruitment,lat_1=Data_for_enteric_virus$SiteRecruitment
                            )
home_address_1 <- ifelse( map_distance$lon_1== "Dong Thap","105.6882	", ifelse(map_distance$lon_1 == "Dak Lak","108.2378",ifelse(map_distance$lon_1 == "Hue","109.0526","107.5909")))
home_address_2 <- ifelse( map_distance$lat_1== "Dong Thap","10.4938	", ifelse(map_distance$lat_1 == "Dak Lak","12.71001",ifelse(map_distance$lat_1 == "Hue","12.25851","16.46371	")))
map_distance$lon_1 <- home_address_1
map_distance$lat_1 <- home_address_2
```

## 6.map(home-red and hospital-blue) 
```{r}
register_google(key="AIzaSyCdg-FnupzUEEAM45jJFOYMvX_gDFZUk7g")
geocode("Vietnam")
geocode("Vietnam Dong Thap")
geocode("Vietnam Dak Lak")
geocode("Vietnam Khanh Hoa")
geocode("Vietnam Hue")
map_distance$lon_1 <- as.numeric(map_distance$lon_1)
map_distance$lat_1 <- as.numeric(map_distance$lat_1)
ggmap(get_map("Vietnam",zoom=6))+geom_point(data=map_distance,aes(x=lon,y=lat),colour = 'red4',alpha=0.7) + geom_point(data=map_distance,aes(x=lon_1,y=lat_1),alpha=0.7,color='blue')
# vietman lon=108.2772,lat=14.05832
```

## 7 distribution of six common viruses
```{r}
common_virus_homelocation <- data.frame(CentrallyCity=Data_for_enteric_virus$CentrallyCity,lon=Data_for_enteric_virus$LONGITUDE,lan=Data_for_enteric_virus$LATITUDE,Rotavirus=Data_for_enteric_virus$Rotavirus,Norovirus=Data_for_enteric_virus$Norovirus, Aichivirus=Data_for_enteric_virus$Kobuvirus, Adenovirus=Data_for_enteric_virus$Mastadenovirus,Sapovirus=Data_for_enteric_virus$Sapovirus, Astrovirus=Data_for_enteric_virus$Mamastrovirus
                            )
#choose 1(positive) for every common viruses
a<-common_virus_homelocation[which(common_virus_homelocation$Rotavirus=="Yes"),]
b<-common_virus_homelocation[which(common_virus_homelocation$Norovirus=="Yes" ),]
c<-common_virus_homelocation[which(common_virus_homelocation$Aichivirus=="Yes"),]
d<-common_virus_homelocation[which(common_virus_homelocation$Adenovirus=="Yes"),]
e<-common_virus_homelocation[which(common_virus_homelocation$Sapovirus=="Yes"),]
f<-common_virus_homelocation[which(common_virus_homelocation$Astrovirus=="Yes"),]

#1.Rotavirus all in "Dong Thap"
#2.Norovirus 69 Dong Thap 
b_1 <- b[which(b$CentrallyCity=="Dong Thap"),]
length(b_1$CentrallyCity)
#count
length(a$Rotavirus)
length(b$Norovirus)
length(c$Aichivirus)
length(d$Adenovirus)
length(e$Sapovirus)
length(f$Astrovirus)
```

## map continue
```{r}
#par(mfrow=c(2,1))
#n=151
ggmap(get_googlemap("Vietnam Dong Thap", zoom=9,
maptype='roadmap'),extent = 'device')+
  geom_point(data=a,aes(x=lon,y=lan,fill=Rotavirus),
colour = 'red4',alpha=0.7)+ geom_point(data=map_distance,aes(x=lon_1,y=lat_1),alpha=0.7,color='blue')
```

```{r}
#n=89
ggmap(get_googlemap("Vietnam", zoom=6,
maptype='roadmap'),extent = 'device')+
  geom_point(data=b,aes(x=lon,y=lan,fill=Norovirus),
colour = 'red4',alpha=0.7)
```

```{r}
#n=5
ggmap(get_googlemap("Vietnam Dong Thap", zoom=9,
maptype='roadmap'),extent = 'device')+
  geom_point(data=c,aes(x=lon,y=lan,fill=Aichivirus),
colour = 'red4',alpha=0.7)
``` 

```{r}
#n=51
ggmap(get_googlemap("Vietnam", zoom=6,
maptype='roadmap'),extent = 'device')+
  geom_point(data=d,aes(x=lon,y=lan,fill=Adenovirus),
colour = 'red4',alpha=0.7)
```

```{r}
#n=57
ggmap(get_googlemap("Vietnam", zoom=6,
maptype='roadmap'),extent = 'device')+
  geom_point(data=e,aes(x=lon,y=lan,fill=Sapovirus),
colour = 'red4',alpha=0.7)
```

```{r}
#n=22
ggmap(get_googlemap("Vietnam", zoom=6,
maptype='roadmap'),extent = 'device')+
  geom_point(data=f,aes(x=lon,y=lan,fill=Astrovirus),
colour = 'red4',alpha=0.7)
```

## 8 gender
```{r}
pie_data2 <- Data_for_enteric_virus[,'Gender']
tab2 <- table(pie_data2)
tab2 <- as.data.frame(tab2)
colnames(tab2) <- c('gender','numb');tab2
p3 <- ggplot(tab2,aes(x='',y=numb,fill=gender)) +
      geom_bar(stat = 'identity', width = 1) +
      theme_bw() +scale_fill_manual(values=c("lightblue", "grey"))+
      labs(x = '', y = '',title = 'Number of respondents with different gender') 
p3
p4 <- p3 + coord_polar(theta = 'y', start = 0, direction = 1)
p4
```

## 9 Age
```{r}
scatt_data <- Data_for_enteric_virus[,'Age']
tab3 <- table(scatt_data)
tab3 <- as.data.frame(tab3)
colnames(tab3) <- c('age','numb');tab3
ggplot(tab3,mapping=aes(x=age,y=numb,fill=age))+
      geom_bar(stat="identity")   
```

## 10 symptons 
```{r}
library(tableone)
pie_data3 <- Data_for_enteric_virus[,c('ContactDiar','BloodStool','MucoidStool','AbdominalPain','ThreeDaysFever')]
tab3 <- CreateCatTable(data = pie_data3,vars = c('ContactDiar','BloodStool','MucoidStool','AbdominalPain','ThreeDaysFever'))
tab3 <- as.data.frame(tab3$Overall)
tab3 <- t(tab3)
write.csv(tab3,file = 'Clinical manifestations.csv')
name01 <- c('ContactDiar','BloodStool','MucoidStool','AbdominalPain','ThreeDaysFever')
```
## 11 contactdiar
```{r}
t_1 <- data_frame(ContactDiar=pie_data3$ContactDiar)
t_1<- t_1[which(t_1$ContactDiar=="Yes"| t_1$ContactDiar=="No"),]
table1 <- table(t_1[,1])
table1 <- as.data.frame(table1)
colnames(table1) <- c(name01[1],'numb');table1
percentage <- scales::percent(table1$numb/sum(table1$numb),accuracy = 0.01)
labs01 <- paste(table1[,1], '(', percentage, ')', sep = '')
p5 <- ggplot(table1,aes(x=' ',y=numb,fill=ContactDiar)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(350, 5), label = labs01)) +
  theme_bw() +scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents contacted with patients') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p5
```

##12 blood stool
```{r}
table2 <- table(pie_data3[,2])
table2 <- as.data.frame(table2)
table2<- table2[which(table2$Var1=="Yes"| table2$Var1=="No"),]
colnames(table2) <- c(name01[2],'numb');table2
percentage <- scales::percent(table2$numb/sum(table2$numb),accuracy = 0.01)
labs02 <- paste(table2[,1], '(', percentage, ')', sep = '')
p6 <- ggplot(table2,aes(x=' ',y=numb,fill=BloodStool)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(350, 5), label = labs02)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Blood Stool') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p6
```

##13 mucoid stool
```{r}
table3 <- table(pie_data3[,3])
table3 <- as.data.frame(table3)
table3<- table3[which(table3$Var1=="Yes"| table3$Var1=="No"),]
colnames(table3) <- c(name01[3],'numb');table3
percentage <- scales::percent(table3$numb/sum(table3$numb),accuracy = 0.01)
labs03 <- paste(table3[,1], '(', percentage, ')', sep = '')
p7 <- ggplot(table3,aes(x=' ',y=numb,fill=MucoidStool)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(350, 5), label = labs03)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Mucoid Stool') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p7
```

##14 abdominal pain
```{r}
table4 <- table(pie_data3[,4])
table4 <- as.data.frame(table4)
table4<- table4[which(table4$Var1=="Yes"| table4$Var1=="No"),]
colnames(table4) <- c(name01[4],'numb');table4
percentage <- scales::percent(table4$numb/sum(table4$numb),accuracy = 0.01)
labs04 <- paste(table4[,1], '(', percentage, ')', sep = '')
p8 <- ggplot(table4,aes(x=' ',y=numb,fill=AbdominalPain)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(500, 150), label = labs04)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Abdominal Pain') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p8
```

##15 Three days fever
```{r}
table5 <- table(pie_data3[,5])
table5 <- as.data.frame(table5)
table5<- table5[which(table5$Var1=="Yes"| table5$Var1=="No"),]
colnames(table5) <- c(name01[5],'numb');table5
percentage <- scales::percent(table5$numb/sum(table5$numb),accuracy = 0.01)
labs05 <- paste(table5[,1], '(', percentage, ')', sep = '')
p9 <- ggplot(table5,aes(x=' ',y=numb,fill=ThreeDaysFever)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(500, 150), label = labs05)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Three-Days Fever') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p9
```

```{r}
library(devtools)
library(ggpubr)
ggarrange(p6,p7,p8,p9,ncol = 2,nrow = 2)
```

##16 Blood description
```{r}
boxplot_data <- Data_for_enteric_virus[,c(23:28)]
name_blood <- read.table('name02.txt',header = F)
name_blood <- as.vector(name_blood$V1)
colnames(boxplot_data) <- name_blood
library(reshape2)
library(knitr)
boxplot_data01 <- melt(boxplot_data,variable.name = 'group',value.name = 'value')
ggplot(boxplot_data01, aes(x=group, y=value)) + geom_boxplot(alpha=0.7) +
       scale_y_continuous(name = "value")+
       scale_x_discrete(name = "Variables") +
       ggtitle("Statistical description of blood routine examination") +
       theme_bw() +
       theme(plot.title = element_text(size = 14, face =  "bold"),
        text = element_text(size = 12),
        axis.title = element_text(face="bold"),
        axis.text.x=element_text(size = 11)) 
```


##17 water resources
```{r}
water_data <- Data_for_enteric_virus[,c(31:37)]
name02 <- c('Tap','Well','Rain','River','Pond','Bottled','OtherWS')
```

##tap
```{r}
wat_tab1 <- table(water_data[,1])
wat_tab1 <- as.data.frame(wat_tab1)
colnames(wat_tab1) <- c(name02[1],'numb');wat_tab1
percentage <- scales::percent(wat_tab1$numb/sum(wat_tab1$numb),accuracy = 0.01)
wat_labs01 <- paste(wat_tab1[,1], '(', percentage, ')', sep = '')
p11 <- ggplot(wat_tab1,aes(x=' ',y=numb,fill=Tap)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(500, 200), label = wat_labs01)) +
  theme_bw() +  scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents drank water from taps') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p11
```

#Well
```{r}
wat_tab2 <- table(water_data[,2])
wat_tab2 <- as.data.frame(wat_tab2)
colnames(wat_tab2) <- c(name02[2],'numb');wat_tab2
percentage <- scales::percent(wat_tab2$numb/sum(wat_tab2$numb),accuracy = 0.01)
wat_labs02 <- paste(wat_tab2[,1], '(', percentage, ')', sep = '')
p12 <- ggplot(wat_tab2,aes(x=' ',y=numb,fill=Well)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(500, 5), label = wat_labs02)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents drank water from well') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p12
```

#Rain
```{r}
wat_tab3 <- table(water_data[,3])
wat_tab3 <- as.data.frame(wat_tab3)
colnames(wat_tab3) <- c(name02[3],'numb');wat_tab3
percentage <- scales::percent(wat_tab3$numb/sum(wat_tab3$numb),accuracy = 0.01)
wat_labs03 <- paste(wat_tab3[,1], '(', percentage, ')', sep = '')
p13 <- ggplot(wat_tab3,aes(x=' ',y=numb,fill=Rain)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(500, 5), label = wat_labs03)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents drank water from Rain') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p13
```

#River
```{r}
wat_tab4 <- table(water_data[,4])
wat_tab4 <- as.data.frame(wat_tab4)
colnames(wat_tab4) <- c(name02[4],'numb');wat_tab4
percentage <- scales::percent(wat_tab4$numb/sum(wat_tab4$numb),accuracy = 0.01)
wat_labs04 <- paste(wat_tab4[,1], '(', percentage, ')', sep = '')
p14 <- ggplot(wat_tab4,aes(x=' ',y=numb,fill=River)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(500, 100), label = wat_labs04)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents drank water from River') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p14
```

#Pond
```{r}
wat_tab5 <- table(water_data[,5])
wat_tab5 <- as.data.frame(wat_tab5)
colnames(wat_tab5) <- c(name02[5],'numb');wat_tab5
percentage <- scales::percent(wat_tab5$numb/sum(wat_tab5$numb),accuracy = 0.01)
wat_labs05 <- paste(wat_tab5[,1], '(', percentage, ')', sep = '')
p15 <- ggplot(wat_tab5,aes(x=' ',y=numb,fill=Pond)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(500, 1), label = wat_labs05)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents drank water from Pond') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p15
```

#Bottled
```{r}
wat_tab6 <- table(water_data[,6])
wat_tab6 <- as.data.frame(wat_tab6)
colnames(wat_tab6) <- c(name02[6],'numb');wat_tab6
percentage <- scales::percent(wat_tab6$numb/sum(wat_tab6$numb),accuracy = 0.01)
wat_labs06 <- paste(wat_tab6[,1], '(', percentage, ')', sep = '')
p16 <- ggplot(wat_tab6,aes(x=' ',y=numb,fill=Bottled)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(500, 100), label = wat_labs06)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents drank Bottled water') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p16
```

#otherWS
```{r}
wat_tab7 <- table(water_data[,7])
wat_tab7 <- as.data.frame(wat_tab7)
colnames(wat_tab7) <- c(name02[7],'numb');wat_tab7
percentage <- scales::percent(wat_tab7$numb/sum(wat_tab7$numb),accuracy = 0.01)
wat_labs07 <- paste(wat_tab7[,1], '(', percentage, ')', sep = '')
p17 <- ggplot(wat_tab7,aes(x=' ',y=numb,fill=OtherWS)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(350), label = wat_labs07)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents drank water from other water sources') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p17
```

```{r}
ggarrange(p11,p12,p13,p14,p15,p16,ncol=3,nrow=2)
```

##18 animal contact
```{r}
animal_data <- Data_for_enteric_virus[,c(38:40)]
name03 <- c('KeepAnimal','KillingAnimal','EatCookRawMeat')
```

#KeepAnimal
```{r}
mate_tab1 <- table(mate_data[,1])
mate_tab1 <- as.data.frame(mate_tab1)
colnames(mate_tab1) <- c(name03[1],'numb');mate_tab1
percentage <- scales::percent(mate_tab1$numb/sum(mate_tab1$numb),accuracy = 0.01)
mate_labs01 <- paste(mate_tab1[,1], '(', percentage, ')', sep = '')
p17 <- ggplot(mate_tab1,aes(x=' ',y=numb,fill=KeepAnimal)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(500,150), label = mate_labs01)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents keeping Animal') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p17
```

#KillingAnimal
```{r}
mate_tab2 <- table(mate_data[,2])
mate_tab2 <- as.data.frame(mate_tab2)
colnames(mate_tab2) <- c(name03[2],'numb');mate_tab2
percentage <- scales::percent(mate_tab2$numb/sum(mate_tab2$numb),accuracy = 0.01)
mate_labs02 <- paste(mate_tab2[,1], '(', percentage, ')', sep = '')
p18 <- ggplot(mate_tab2,aes(x=' ',y=numb,fill=KillingAnimal)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(500,10), label = mate_labs02)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents Killing Animal') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p18
```

#EatRawMeat
```{r}
mate_tab3 <- table(mate_data[,3])
mate_tab3 <- as.data.frame(mate_tab3)
colnames(mate_tab3) <- c(name03[3],'numb');mate_tab3
percentage <- scales::percent(mate_tab3$numb/sum(mate_tab3$numb),accuracy = 0.01)
mate_labs03 <- paste(mate_tab3[,1], '(', percentage, ')', sep = '')
p19 <- ggplot(mate_tab3,aes(x=' ',y=numb,fill=EatCookRawMeat)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(600,250), label = mate_labs03)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents Eating Raw Meat') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p19
```

## 19 Bacterial
```{r}
bact_data <- as.data.frame(Data_for_enteric_virus[,c('IF_Bacterial')])
bact_tab <- table(bact_data[,1])
bact_tab <- as.data.frame(bact_tab);bact_tab
colnames(bact_tab) <- c('IF_Bacterial','numb');bact_tab
percentage <- scales::percent(bact_tab$numb/sum(bact_tab$numb),accuracy = 0.01)
bact_lab01 <- paste(bact_tab[,1], '(', percentage, ')', sep = '')
p21 <- ggplot(bact_tab,aes(x=' ',y=numb,fill=IF_Bacterial)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(400,25), label = bact_lab01)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents with pathogens tested positive') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p21
```

## 20 viruses
```{r}
chart_data <- Data_for_enteric_virus[,c(56:87)]
name04 <- c('Alphapapillomavirus','Alphapolyomavirus','Alphatorquevirus','Betapapillomavirus','Betapolyomavirus','Betatorquevirus','Bocaparvovirus','Cardiovirus','Circovirus','Cosavirus','Cytomegalovirus','Enterovirus','Gammatorquevirus','Gemycircularvirus','Gemykibivirus','Gemykrogvirus','Husavirus','Kobuvirus','Lymphocryptovirus','Mamastrovirus','Mastadenovirus','Morbillivirus','Norovirus','Parechovirus','Picobirnavirus','Porprismacovirus','Protoparvovirus','Rotavirus','Rubulavirus','Salivirus','Sapovirus','Unclassified virus')
#name04 <- read.table('name02.txt',header = F)
#name04 <- as.vector(name04$V1)
colnames(chart_data) <- name04
tab4 <- CreateCatTable(data = chart_data,vars = name04)
tab5 <- as.list(tab4$Overall)
tab6 <- tab5[[name04[1]]]
for (i in 2:32){
  tab7 <- tab5[[name04[i]]]
  tab6 <- rbind(tab6,tab7)
}
write.csv(tab6,file = 'viruses.csv')
```

# common viruses (plot)
```{r}
common_virus <- Data_for_enteric_virus[,c(73,75,76,78,83,86)]
name05 <- c('Kobuvirus','Mamastrovirus','Mastadenovirus','Norovirus','Rotavirus','Sapovirus')
colnames(common_virus) <- name05
common_virus_tab1 <- table(common_virus[,1])
common_virus_tab1 <- as.data.frame(common_virus_tab1);common_virus_tab1
colnames(common_virus_tab1) <- c('Kobuvirus','numb');common_virus_tab1
percentage <- scales::percent(common_virus_tab1$numb/sum(common_virus_tab1$numb),accuracy = 0.01)
common_virus_lab01 <- paste(common_virus_tab1[,1], '(', percentage, ')', sep = '')
p22 <- ggplot(common_virus_tab1,aes(x=' ',y=numb,fill=Kobuvirus)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(350,1), label = common_virus_lab01)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents infected by Kobuvirus') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p22
```

```{r}
common_virus_tab2 <- table(common_virus[,2])
common_virus_tab2 <- as.data.frame(common_virus_tab2);common_virus_tab2
colnames(common_virus_tab2) <- c('Mamastrovirus','numb');common_virus_tab2
percentage <- scales::percent(common_virus_tab2$numb/sum(common_virus_tab2$numb),accuracy = 0.01)
common_virus_lab02 <- paste(common_virus_tab2[,1], '(', percentage, ')', sep = '')
p23 <- ggplot(common_virus_tab2,aes(x=' ',y=numb,fill=Mamastrovirus)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(350,10), label = common_virus_lab02)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents infected by Mamastrovirus') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p23
```

```{r}
common_virus_tab3 <- table(common_virus[,3])
common_virus_tab3 <- as.data.frame(common_virus_tab3);common_virus_tab3
colnames(common_virus_tab3) <- c('Mastadenovirus','numb');common_virus_tab3
percentage <- scales::percent(common_virus_tab3$numb/sum(common_virus_tab3$numb),accuracy = 0.01)
common_virus_lab03 <- paste(common_virus_tab3[,1], '(', percentage, ')', sep = '')
p24 <- ggplot(common_virus_tab3,aes(x=' ',y=numb,fill=Mastadenovirus)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(350,25), label = common_virus_lab03)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents infected by Mastadenovirus') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p24
```

```{r}
common_virus_tab4 <- table(common_virus[,4])
common_virus_tab4 <- as.data.frame(common_virus_tab4);common_virus_tab4
colnames(common_virus_tab4) <- c('Norovirus','numb');common_virus_tab4
percentage <- scales::percent(common_virus_tab4$numb/sum(common_virus_tab4$numb),accuracy = 0.01)
common_virus_lab04 <- paste(common_virus_tab4[,1], '(', percentage, ')', sep = '')
p25 <- ggplot(common_virus_tab4,aes(x=' ',y=numb,fill=Norovirus)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(350,25), label = common_virus_lab04)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents infected by Norovirus') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p25
```

```{r}
common_virus_tab5 <- table(common_virus[,5])
common_virus_tab5 <- as.data.frame(common_virus_tab5);common_virus_tab5
colnames(common_virus_tab5) <- c('Rotavirus','numb');common_virus_tab5
percentage <- scales::percent(common_virus_tab5$numb/sum(common_virus_tab5$numb),accuracy = 0.01)
common_virus_lab05 <- paste(common_virus_tab5[,1], '(', percentage, ')', sep = '')
p26 <- ggplot(common_virus_tab5,aes(x=' ',y=numb,fill=Rotavirus)) +
  geom_bar(stat = 'identity', width = 1) +
  geom_text(aes(y = c(375,75), label = common_virus_lab05)) +
  theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
  labs(x = '', y = '',title = 'Number of respondents infected by Rotavirus') +
  coord_polar(theta = 'y', start = 0, direction = 1)
p26
```

```{r}
common_virus_tab6 <- table(common_virus[,6])
common_virus_tab6 <- as.data.frame(common_virus_tab6);common_virus_tab6
colnames(common_virus_tab6) <- c('Sapovirus','numb');common_virus_tab6
percentage <- scales::percent(common_virus_tab6$numb/sum(common_virus_tab6$numb),accuracy = 0.01)
common_virus_lab06 <- paste(common_virus_tab6[,1], '(', percentage, ')', sep = '')
p27 <- ggplot(common_virus_tab6,aes(x=' ',y=numb,fill=Sapovirus)) +
              geom_bar(stat = 'identity', width = 1) +
              geom_text(aes(y = c(375,75), label = common_virus_lab06)) +
              theme_bw() + scale_fill_manual(values=c("lightblue", "grey"))+
              labs(x = '', y = '',title = 'Number of respondents infected by Sapovirus') +
              coord_polar(theta = 'y', start = 0, direction = 1)
p27
```

```{r}
grid.arrange(p22,p23,p24,p25,p26,p27,ncol=3,nrow=2)
```


##21 coinfections
```{r}
coinfect_data <- Data_for_enteric_virus[,'is_coinf']
tab8 <- table(coinfect_data)
tab8 <- as.data.frame(tab8)
colnames(tab8) <- c('is_coinf','numb');tab8
ggplot(tab8,mapping=aes(x=is_coinf,y=numb,width=0.5,fill=is_coinf))+
  geom_bar(stat="identity")
```


## coinfection regression model 01
```{r}
regres_data <- Data_for_enteric_virus[,c(3,8,9,12,13,17:28,31:36,38:41,88)]
write.csv(regres_data,file = 'regression data02.csv')
regres_data02 <- read.csv('regression data02.csv',header = T)
regres_data02 <- regres_data02[,-1]
model<-lm(is_coinf~.,data=regres_data)
summary(model)
```


```{r}
name06 <- c('Age','SiteRecruitment','Gender','Length of stay','CentrallyCity','ContactDiar','BloodStool','MucoidStool','NumberDiarEpi','AbdominalPain','ThreeDaysFever','HaemoglobinResult','WhiteCellsResult','NeutrophilsResult','LymphocytesResult','EosinophilsResult','PlateletsResult','Tap','Well','Rain','River','Pond','Bottled','KeepAnimal','KillingAnimal','EatCookRawMeat','IF_Bacterial','is_coinf')
name06 <- as.vector(name06)
regres_data <- Data_for_enteric_virus[,c(3,8,9,12,13,17:28,31:36,38:41,88)]
colnames(regres_data) <- name06
write.csv(regres_data,file = 'regression data02.csv')
regres_data02 <- read.csv('regression data02.csv',header = T)
regres_data02 <- regres_data02[,-1]
model<-lm(is_coinf~.,data=regres_data02)
summary(model)
```

```{r}
library(MASS)
#name06 <- read.table('name02.txt',header = F)
#name06 <- as.vector(name06$V1)
regres_data <- Data_for_enteric_virus[,c(3,8,9,12,13,17:28,30:41,73,75,76,78,83,86,88)]
colnames(regres_data) <- name06
regres_data <- regres_data[,-24]
#regres_data[,c(18:23)] <- as.factor(regres_data[,c(18:23)])
write.csv(regres_data,file = 'regression data03.csv')
regres_data01 <- read.csv('regression data03.csv',header = T)
regres_data01 <- regres_data01[,-1]
regres_data01[,2] <- as.factor(regres_data01[,2])
name07 <- as.vector(colnames(regres_data01))
```

# ordinal regression model (delete)
```{r}
library(leaps)
model2 <- regsubsets(is_coinf ~ Age+SiteRecruitment+Gender+HaemoglobinResult+WhiteCellsResult+Well+IF_Bacterial, data = regres_data02,nbest = 7)
plot(model2,scale='r2')
summary(model2)
model3 <- lm(is_coinf ~ Age+SiteRecruitment+Gender+HaemoglobinResult+WhiteCellsResult+Well+IF_Bacterial, data = regres_data02)
summary(model3)
model4<-step(model3,direction = "backward")
summary(model4)
regres_data01[,c(2,3,5:7,9,10,18:28)] <- as.factor(regres_data01[,c(2,3,5:7,9,10,18:28)])
model5 <- polr(as.factor(is_coinf) ~ Age+HaemoglobinResult+WhiteCellsResult+LymphocytesResult+EatCookRawMeat+IF_Bacterial, data = regres_data02)
summary(model5,digits = 3)
```


##22 multinomial linear regression model
```{r}
library(nnet)
regres_data4 <- Data_for_enteric_virus[,c(3,13,17,31:36,38:40,88)]
regres_data4$is_coinf <- as.factor (regres_data4$is_coinf)
table(regres_data4$is_coinf) #check the output dependent variable
regres_data4$is_coinf <- relevel(regres_data4$is_coinf, ref= "0") # change it, "0" is the reference type
```

```{r}
multi1 <- multinom(data=regres_data4,formula = is_coinf ~ Age +CentrallyCity+ContactDiar+Tap+Well+Rain+River+Pond+Bottled+KeepAnimal+KillingAnimal+EatCookRawMeat)
summary(multi1)
write.csv(multi1$residuals,file = 'multiregression result1.csv')
```


```{r}
library(stargazer)
stargazer(multi1,type = "text",out = "multi1.text")
```

```{r}
multi1.r <- exp(coef(multi1))
multi1.r 
```

```{r}
library(stargazer)
stargazer(multi1,type = "text",coef=list(multi1.r),p.auto=FALSE, out = "multi1r.text")
```

# multi2 (coinfection combinations)
```{r}
#multi_data <- read_excel("multi data.xlsx")
#multi_data$is_coinf <- as.numeric(multi_data$is_coinf)
index <- which(multi_data$is_coinf==3|multi_data$is_coinf==4|multi_data$is_coinf==5)
multi_data[index,]$is_coinf = " $>= 3$ coinfections"
regres_data4_2 <- multi_data[,c(3,13,17,31:36,38:40,88)]
#regres_data4_2 <- which(regres_data4_2$is_coinf=="NA")
#regres_data4_2 <- ifelse(regres_data4_2$is_coinf=="NA",0)
table(multi_data$is_coinf)  # 1 is the reference type
#regres_data4$is_coinf <- relevel(regres_data4$is_coinf, ref= "0") 
```

```{r}
multi2 <- multinom(data=regres_data4_2,formula = is_coinf ~ Age +CentrallyCity+ContactDiar+Tap+Well+Rain+River+Pond+Bottled+KeepAnimal+KillingAnimal+EatCookRawMeat)
summary(multi2)
write.csv(multi2$residuals,file = 'multiregression result2.csv')
```

```{r}
library(stargazer)
stargazer(multi2,type = "text",out = "multi2.text")
```


## 23 what are the risk factors associated with the common viruses? logit model
#1 Kobuvirus 
```{r}
bio_1 <- Data_for_enteric_virus[,c(3,13,17,31:36,38:40,73)]
bio_1$Kobuvirus <- as.factor(bio_1$Kobuvirus)
table(bio_1$Kobuvirus) # check the output dependent variable
bio1_model <- glm(data=bio_1, Kobuvirus  ~ Age +CentrallyCity+ContactDiar+Tap+Well+Rain+River+Pond+Bottled+KeepAnimal+KillingAnimal+EatCookRawMeat,family = binomial(link = "logit"))
summary(bio1_model)
```

# adjust data
```{r}
#logit_data <- read_excel("Desktop/logit data.xlsx")
bio_12 <- logit_data[,c(3,13,17,31:36,38:40,73)]
index2 <- which(logit_data$CentrallyCity=="Dak Lak"|logit_data$CentrallyCity=="Dak Nong"|logit_data$CentrallyCity=="Khanh Hoa"|logit_data$CentrallyCity=="Quang Binh"|logit_data$CentrallyCity=="Quang Tri"|logit_data$CentrallyCity=="Thua Thien - Hue")
bio_12[index2,]$CentrallyCity = " other locations"
#contact_update <- which(logit_data$ContactDiar==1|logit_data$ContactDiar==2)
#bio_12$ContactDiar <- contact_update
logit_data$Kobuvirus <- as.factor(logit_data$Kobuvirus)
bio12_model <- glm(data=bio_12, Kobuvirus  ~ Age +CentrallyCity+ContactDiar+Tap+Well+Rain+River+Pond+Bottled+KeepAnimal+KillingAnimal+EatCookRawMeat,family = binomial(link = "logit"))
summary(bio12_model)
#index2 <- which(bio_1$CentrallyCity=="Dak Lak"|bio_1$CentrallyCity=="Dak Nong"|bio_1$CentrallyCity=="Khanh Hoa"|bio_1=="Quang Binh"|bio_1=="Quang Tri"|bio_1=="Thua Thien-Hue")
#bio_1[index2,]$CentrallyCity = " other locations"
#regres_data4_2 <- multi_data[,c(3,13,17,31:36,38:40,88)]
```

# choose（Age）
```{r}
update_bio1 <- glm(Kobuvirus~1,family = binomial(link = "logit"),data=bio_1)
logit.bio1 <- step(update_bio1,scope = formula(bio1_model),direction = "both",trace = F)
summary(logit.bio1) 
```

```{r}
library(stargazer)
stargazer(bio1_model,type = "text",out = "bio1_model.text")
```

```{r}
library(stargazer)
stargazer(logit.bio1,type = "text",out = "logit.bio1.text")
```

```{r}
exp(coef(logit.bio1))
```

#2 Mamastrovirus # Well
```{r}
bio_2 <- Data_for_enteric_virus[,c(3,13,17,31:36,38:40,75)]
bio_2$Mamastrovirus <- as.factor(bio_2$Mamastrovirus)
bio2_model <- glm(data=bio_2, Mamastrovirus  ~ Age +CentrallyCity+ContactDiar+Tap+Well+Rain+River+Pond+Bottled+KeepAnimal+KillingAnimal+EatCookRawMeat,family = binomial(link = "logit"))   #Well
summary(bio2_model)
```

```{r}
#choose fron bio2_model automatically
update_bio2 <- glm(Mamastrovirus ~ 1,family = binomial(link = "logit"),data=bio_2)
logit.bio2 <- step(update_bio2,scope = formula(bio2_model),direction = "both",trace = F)
summary(logit.bio2) #KeepAnimalYes
```

```{r}
stargazer(bio2_model,type = "text",out = "bio2_model.text")
```

```{r}
stargazer(logit.bio2,type = "text",out = "logit.bio2.text")
```

```{r}
bio2_model2 <- glm(data=bio_2, Mamastrovirus  ~ Well+KeepAnimal,family = binomial(link = "logit"))   #Well
summary(bio2_model2)
stargazer(bio2_model2,type = "text",out = "bio2_model2.text")
final_model <- exp(coef(bio2_model2))
stargazer(final_model,type = "text",out = "final_model.text")
```


#3 Mastadenovirus #Age
```{r}
bio_3 <- Data_for_enteric_virus[,c(3,13,17,31:36,38:40,76)]
bio_3$Mastadenovirus <- as.factor(bio_3$Mastadenovirus)
bio3_model <- glm(data=bio_3, Mastadenovirus  ~ Age +CentrallyCity+ContactDiar+Tap+Well+Rain+River+Pond+Bottled+KeepAnimal+KillingAnimal+EatCookRawMeat,family = binomial(link = "logit"))
summary(bio3_model)
```

#choose automatically 
```{r}
update_bio3 <- glm(Mastadenovirus ~ 1,family = binomial(link = "logit"),data=bio_3)
logit.bio3 <- step(update_bio3,scope = formula(bio3_model),direction = "both",trace = F)
summary(logit.bio3)
```

```{r}
stargazer(bio3_model,type = "text",out = "bio3_model.text")
```

```{r}
stargazer(logit.bio3,type = "text",out = "logit.bio3.text")
```

#Age is significant logit
```{r}
bio_3_1 <- bio_3[,c(1,13)]
bio3_model_1 <- glm(data=bio_3_1, Mastadenovirus  ~ Age,family = binomial(link = "logit"))
summary(bio3_model_1)
```

```{r}
stargazer(bio3_model_1,type = "text",out = "bio3_model_1.text")
exp(coef(bio3_model_1))
```

#4 Norovirus (Age,Dong Thap ) # Firth's penalised likelihood
```{r}
bio_4 <- Data_for_enteric_virus[,c(3,13,17,31:36,38:40,78)]
bio_4$Norovirus <- as.factor(bio_4$Norovirus)
bio4_model <- glm(data=bio_4, Norovirus  ~ Age +CentrallyCity+ContactDiar+Tap+Well+Rain+River+Pond+Bottled+KeepAnimal+KillingAnimal+EatCookRawMeat,family = binomial(link = "logit"))
summary(bio4_model)
#library(logistf)     #Firth's penalised likelihood
#h1 <- logistf(data=bio_4,Norovirus  ~ Age +CentrallyCity)
#summary(h1)
```
#continue logit
```{r}
bio_4_1 <- bio_4[,c(1,2,13)]
#CentrallyCity<-bio_4_1[which(bio_4_1$CentrallyCity=="Dong Thap"|bio_4_1$CentrallyCity=="Dak Nong"|bio_4_1$CentrallyCity=="Khanh Hoa"),]
#bio_4_1$Norovirus <- as.factor(bio_4_1$Norovirus)
bio4_model1 <- glm(data=CentrallyCity, Norovirus  ~ Age + CentrallyCity, family = binomial(link = "logit"))
summary(bio4_model1)
```

# DONG THAP logit
```{r}
bio_4_11 <- CentrallyCity[,c(2,3)]
bio4_model1_update <- glm(data=bio_4_11, Norovirus  ~ CentrallyCity, family = binomial(link = "logit"))
summary(bio4_model1_update)
coef(bio4_model1_update)
```

# compare model
```{r}
anova(bio4_model1_update,bio4_model1,test = "Chisq")
```

```{r}
stargazer(bio4_model,type = "text",out = "bio4_model.text")
```

```{r}
stargazer(bio4_model1,type = "text",out = "bio4_model1.text")
```

```{r}
stargazer(bio4_model1_update,type = "text",out = "bio4_model1_update.text")
```

```{r}
exp_model4 <-exp(coef(bio4_model1_update))
stargazer(exp_model4,type = "text",out = "bio4_model1_update.text")
#Age,ContactDiar,River, Bottle
```

#5  Rotavirus 
```{r}
bio_5 <- Data_for_enteric_virus[,c(3,13,17,31:36,38:40,83)]
bio_5$Rotavirus <- as.factor(bio_5$Rotavirus)
bio5_model <- glm(data=bio_5, Rotavirus  ~ Age +CentrallyCity+ContactDiar+Tap+Well+Rain+River+Pond+Bottled+KeepAnimal+KillingAnimal+EatCookRawMeat,family = binomial(link = "logit"))
summary(bio5_model)
```

```{r}
stargazer(bio5_model,type = "text",out = "bio5_model.text")
```

# Age,ContactDiar,River, Bottle 
```{r}
bio_5_1 <- bio_5[,c(1,3,7,9,13)]
bio_5_1$Rotavirus <- as.factor(bio_5_1$Rotavirus)
#table(bio_5_1$ContactDiar)
bio5_model1 <- glm(data=bio_5_1, Rotavirus  ~ Age +ContactDiar+River+Bottled,family = binomial(link = "logit"))
summary(bio5_model1)
coef(bio5_model1)
```

```{r}
stargazer(bio5_model1,type = "text",out = "bio5_model1.text")
```
#compare two models
```{r}
anova(bio5_model1,bio5_model,test="Chisq")
```

```{r}
exp_model5 <-exp(coef(bio5_model1))
stargazer(exp_model5,type = "text",out = "exp_model5.text")
```

#predict 
```{r}
testdata5 <- data.frame(rating=c(1,2,3,4,5), Age=mean(bio_5$Age),ContactDiar=mean(bio_5$ContactDiar),River=mean(bio_5$River),Bottled=mean(bio_5$Bottled))
testdata5
#bio5_model12 <- glm(data=bio_5_1, Rotavirus  ~ Age +River+Bottled,family = binomial(link = "logit"))
```

```{r}
bio5_model12 <- glm(data=bio_5_1, Rotavirus  ~ Age,family = binomial(link = "logit"))
#testdata5$Age<-as.factor(testdata5$Age)
#testdata5$River<-as.factor(testdata5$River)
#testdata5$Bottled<-as.factor(testdata5$Bottled)
testdata5$prob <- predict(bio5_model12,newdata = testdata5,type = "response")
testdata5
```

```{r}
testdata5 <-data_frame(rating=mean(bio_5$rating),Age=seq(1,2,4))
testdata5
```

#6 Sapovirus #Dong thap, eatcookraw
```{r}
bio_6 <- Data_for_enteric_virus[,c(3,13,17,31:36,38:40,86)]
bio_6$Sapovirus <- as.factor(bio_6$Sapovirus)
bio6_model <- glm(data=bio_6, Sapovirus ~ Age +CentrallyCity+ContactDiar+Tap+Well+Rain+River+Pond+Bottled+KeepAnimal+KillingAnimal+EatCookRawMeat,family = binomial(link = "logit"))
summary(bio6_model)
```

#对 Dong thap,eatcookraw
```{r}
bio_6_1 <- bio_6[,c(2,12,13)]
bio_6_1$Sapovirus <- as.factor(bio_6_1$Sapovirus)
bio6_model1 <- glm(data=bio_6_1, Sapovirus ~ CentrallyCity+EatCookRawMeat,family = binomial(link = "logit"))
summary(bio6_model1)
h2 <- logistf(data=bio_6_1,Sapovirus  ~ EatCookRawMeat +CentrallyCity)
summary(h2)
```

```{r}
stargazer(bio6_model,type = "text",out = "bio6_model.text")
```

```{r}
stargazer(bio6_model1 ,type = "text",out = "bio6_model1.text")
```

```{r}
bio_6_2 <- Data_for_enteric_virus[,c(3,17,31:36,38:40,86)]
bio_6_2$Sapovirus <- as.factor(bio_6_2$Sapovirus)
bio6_model2 <- glm(data=bio_6_2, Sapovirus ~ Age +ContactDiar+Tap+Well+Rain+River+Pond+Bottled+KeepAnimal+KillingAnimal+EatCookRawMeat,family = binomial(link = "logit"))
summary(bio6_model2)
```

```{r}
stargazer(bio6_model2 ,type = "text",out = "bio6_model2.text")
```

```{r}
exp_model6 <-exp(coef(bio6_model))
exp_model6
#stargazer(exp_model6 ,type = "text",out = "exp_model6.text")
```
